Multi-product Batch Processing Time Maximization Problem

### 2023-08-14 manuscript.tex
updating manuscript

\begin{abstract}
In the plastic bag extrusion process, it is necessary to determine the optimal processing time for batches formed by different products, which are processed simultaneously by the same extruder, but with different processing rates. The batch processing time must be determined in order to meet a series of known constraints, such as the limitation for the quantity produced for each product and for the quantity produced for the set of all products in the same batch. In this paper we present this problem as a new combinatorial optimization problem named Multi-product Batch Processing Time Maximization (MBPTM) problem. We also present a mathematical model for the MPBPTM problem and an analytical solution method with polynomial time complexity, which proved to be able to obtain optimal solutions for several benchmarks in a very short time, even for very large instances.
\end{abstract}
%%Graphical abstract
\begin{graphicalabstract}
\includegraphics[width=0.8\textwidth]{graphical.png}
\end{graphicalabstract}

@@

\begin{keyword}
multiproduct batch \sep processing time maximization \sep analytical solution \sep C++ \sep LINGO
\end{keyword}
\end{frontmatter}

@@

@@

As scientific contributions, in this paper we define a new multi-product batch problem, named multi-product batch processing time maximization (MPBPTM) problem, as well as a mathematical model and a polynomial time complexity analytical solution optmization method for solving this problem.

@@

The multi-product batch processing time maximization problem arises when a set of different products are processed simultaneously in a same production batch. In this problem, it is considered that the quantity produced of each product is directly proportional to the processing time, however, with a different constant of proportionality (production rate) for each product. In addition, there is a maximum quantity allowed for the production of batch products, defined both individually and for the set. The maximum production quantity of each product is mainly defined according to the demand for the product. However, it is still possible to stock the products and/or send them to the outlets. In both cases, there is a stocking/shipping limit for each product and a stocking/shipping limit for the set of products in the batch. Also, there is a time limit available for processing the batch. About the production, the industry manager has as priority to meet demand and he prefer to send the remaining production to outlets rather then stock it in the factory.

@@

Constraints in (2) relate the quantity produced, $P_i$, to batch processing time $T$. Constraints in (3) calculate the quantity produced, $P_i$, as a function of the primary variables, $D_i$, $O_i$ and $I_i$. Constraints in (4), (5), and (7) state that the quantity delivered to demand, the quantity shipped to the autlets, and the factory-stocked quantity of each product must be less than their respective known limits. Constraints (6) and (8) state that both the sum of product quantities sent to the autlets and the sum of product quantities stocked in the factory must be less than their respective maximum allowed values. The restriction in (9) establishes that there is a batch processing time limit, $\textrm{Z}$, that must be respected. As equações em (10) e (11) definem a prioridade de distribuição da produção. And finally, the constraints in (12) inform the nature of the decision variables.

@@

To solve the MBPTM problem we will start considering that, despite equations in (10) and (11) define a priority for production distribution, $T$ is not affected by the way production is distributed betwing demand, outlets and factory inventory. So we can find $T$, by ignoring this equations and, after finding $T$ for the relaxed model, use this eqautions for distribute the production based on the defined priorities.

Then, it is possible to consider the factory stock and the outlets stock as single stock, so we have:

@@

\begin{equation}
D_i + O_i + I_i = P_i \quad \forall i
\end{equation}

@@

Randomly generated benchmarks were named RMBPTM $\textrm{N}$, being $\textrm{N}$ the number of products. Seeking to enable the reproduction of the results, in the computational construction of the benchmarks we used the function srand((unsigned) source), where source is a defined value. To build the results presented in this work, we used source=0. The benchmarks used for the tests performed can be consulted at github.com/blinded.

@@

\begin{table}[h]
\begin{center}
\begin{footnotesize}
\begin{tabular}[c]{l r r r r}
problem & LINGO solver & time (s) & analytical method & time (s) \\
\cline {1-5} \\
MBPTM 2 & 55 & 0.04 & 55 & 0.001 \\
MBPTM 3 & 48 & 0.06 & 48 & 0.001 \\
MBPTM 10 & 30 & 0.09 & 30 & 0.001 \\
RMBPTM 20 & 100 & 0.08 & 100 & 0.001 \\
RMBPTM 50 & 98 & 0.12 & 98 & 0.001\\
RMBPTM 100 & 98 & 0.12 & 98 & 0.002\\
RMBPTM 1,000 & 78 & 3.10 & 78 & 0.002\\
RMBPTM 10,000 & 70 & 168.87 & 70 & 0.006 \\
\cline {1-5} \\
\end{tabular}
\caption{Results obtained with the LINGO solver and the analytical method}
\label{tab:results}
\end{footnotesize}
\end{center}
\end{table}

>>>>

\begin{abstract}
In the plastic bag extrusion process, it is necessary to determine the optimal processing time for batches formed by different products, which are processed simultaneously by the same extruder, but with different processing rates. The batch processing time must be determined in order to meet a series of known constraints, such as the limitation for the quantity produced for each product and for the quantity produced for the set of all products in the same batch. In this paper we present this problem as a new combinatorial optimization problem named Multi-product Batch Processing Time Maximization (MBPTM) problem. We also present a mathematical model for the MBPTM problem and an analytical solution method with polynomial time complexity, which proved to be able to obtain optimal solutions for several benchmarks in a very short time, even for very large instances.
\end{abstract}
%%Graphical abstract
\begin{graphicalabstract}
\includegraphics[width=0.8\textwidth]{graphical.png}
\end{graphicalabstract}

@@

\begin{keyword}
multiproduct batch \sep processing time maximization \sep mathematical model \sep analytical solution \sep LINGO
\end{keyword}
\end{frontmatter}

@@

Starting a working day... 
Tasks finish tests using LINGO on optimization mode.
Submit paper again to journal.

@@

As scientific contributions, in this paper we define a new multi-product batch problem, named multi-product batch processing time maximization (MBPTM) problem, as well as a mathematical model and a polynomial time complexity analytical solution optmization method for solving this problem.

@@

The multi-product batch processing time maximization problem arises when a set of different products are processed simultaneously in a same production batch. In this problem, it is considered that the quantity produced of each product is directly proportional to the processing time, however, with a different constant of proportionality (production rate) for each product. In addition, there is a maximum quantity allowed for the production of batch products, defined both individually and for the set. The production quantity of each product is mainly defined according to the demand for the product. However, it is still possible to stock the products and/or send them to the outlets. In both cases, there is a stocking/shipping limit for each product and a stocking/shipping limit for the set of products in the batch. Also, there is a time limit available for processing the batch. About the production, the industry manager has as priority to meet demand and he prefer to send the remaining production to outlets rather then stock it in the factory.

@@

Constraints in (2) relate the quantity produced, $P_i$, to batch processing time $T$. Constraints in (3) calculate the quantity produced, $P_i$, as a function of the primary variables, $D_i$, $O_i$ and $I_i$. Constraints in (4), (5), and (7) state that the quantity delivered to demand, the quantity shipped to the autlets, and the factory-stocked quantity of each product must be less than their respective known limits. Constraints (6) and (8) state that both the sum of product quantities sent to the autlets and the sum of product quantities stocked in the factory must be less than their respective maximum allowed values. The restriction in (9) establishes that there is a batch processing time limit, $\textrm{Z}$, that must be respected. Equations in (10) and (11) define the production distribution priority. And finally, the constraints in (12) inform the nature of the decision variables.

@@

To solve the MBPTM problem we will start considering that, despite equations in (10) and (11) define a priority for production distribution, $T$ is not affected by the way production is distributed betwing demand, outlets and factory inventory. So we can find $T$, by ignoring this equations and, after finding $T$ for the relaxed model, solving the production distribution problem based on the defined priorities.

After relaxation of the problem, it is possible to consider the factory stock and the outlets stock as single stock, so we have:

@@

\begin{equation}
D_i + O_i + I_i = p_i*T \quad \forall i
\end{equation}

@@

Randomly generated benchmarks were named RMBPTM $\textrm{N}$, being $\textrm{N}$ the number of products. Seeking to enable the reproduction of the results, in the computational construction of the benchmarks we used the function srand((unsigned) source), where source is a defined value. To build the results presented in this work, we used source=0. The benchmarks used for the tests performed can be consulted at github.com/tbfraga/COPSolver.

@@

\begin{table}[h]
\begin{center}
\begin{footnotesize}
\begin{tabular}[c]{l r r r r}
problem & LINGO solver & time (s) & analytical method & time (s) \\
\cline {1-5} \\
MBPTM 2 & 55 & 0.04 & 55 & 0.001 \\
MBPTM 3 & 48 & 0.06 & 48 & 0.001 \\
MBPTM 10 & 30 & 0.09 & 30 & 0.001 \\
RMBPTM 20 & 100 & 0.10 & 100 & 0.002 \\
RMBPTM 50 & 98 & 0.07 & 98 & 0.002\\
RMBPTM 100 & 98 & 0.11 & 98 & 0.002\\
RMBPTM 1,000 & 78 & 9.59 & 78 & 0.013\\
RMBPTM 2,000 & 70 & 3.24 & 70 & 0.027\\
RMBPTM 5,000 & 70 & 15.28 & 70 & 0.079 \\
RMBPTM 10,000 & 70 & 58.22 & 70 & 0.185 \\
\cline {1-5} \\
\end{tabular}
\caption{Results obtained with the LINGO solver and the analytical method}
\label{tab:results}
\end{footnotesize}
\end{center}
\end{table}
